**First high-frequency time series of carbonate chemistry in the Arctic**

### 2023-05-25 awipev-CO2_presentation.qmd
prez update

---
title: "**First high-frequency time series of carbonate chemistry in the Arctic**" 
author: "Jean-Pierre Gattuso^1,2^, Samir Alliouane^1^ & Philipp Fisher^3^"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  html_document:
    # code_folding: show
    #css: acid.css
    fig_caption: no
    #fig_width: 2
    #fig_height: 2
    highlight: default    
    number_sections: no
    #theme: yeti
    theme: cerulean
    toc: no
    toc_float: no
    fontsize: 32pt
#language: Australian
#css: acid.css
## mainfont: PT Serif  
## monofont: PT Mono
#csl: frontiers.csl
## sansfont: PT Sans
#bibliography: ArcticKelp.bib
## papersize: A4
---
<!-- <style type="text/css"> -->
<!-- .main-container { -->
<!--   max-width: 100% !important; -->
<!--   margin: auto; -->
<!-- } -->
<!-- </style> -->
<style type="text/css">
.main-container {
  max-width: 100% !important;
  margin: auto;
}
h1.title {
  font-size: 50px;
}
body{
  font-size: 24pt;
}
h1,h2,h3,h4,h5,h6{
  font-size: 32pt;
}
h2,h3,h4,h5,h6{
  font-size: 28pt;
}
.blackbox {
  padding: 1em;
  background: LightYellow;
  color: black;
  border: 0px solid orange;
  border-radius: 10px;
}
.center {
  text-align: center;
}
</style>

^1^Laboratoire d'Océanographie de Villefranche, CNRS-Sorbonne Université\
^2^Iddri, Sciences Po\
^3^Alfred Wegener Institute for Polar and Marine Research\

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
  #if (Sys.getenv("LOGNAME") == "gattuso") path = "."
```

![](images/AWIPEV-Logo.jpg){width="500px"}

<br><br><br><br><br><br><br><br><br><br><br><br><br>

:::: {.blackbox data-latex=""}

# **Introduction**

@@

:::: {.blackbox data-latex=""}
# **Instrumental set-up**

>>>>

---
title: "**First high-frequency time series of carbonate chemistry in the Arctic**" 
author: "Jean-Pierre Gattuso^1,2^, Samir Alliouane^1^ & Philipp Fisher^3^"
format:
  revealjs:
    smaller: true
    scrollable: true
editor: visual
---

\^1\^Laboratoire d'Océanographie de Villefranche, CNRS-Sorbonne Université\\
\^2\^Iddri, Sciences Po\\
\^3\^Alfred Wegener Institute for Polar and Marine Research\\

!\[\](images/AWIPEV-Logo.jpg){width="500px"}

## **Introduction**

@@

:::: {.blackbox data-latex=""}
## **Instrumental set-up**
